---
title: "Followup Aalysis"
author: "Xinyue Li"
date: "3/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/Christine/src/mem_dm/Choice_task_analysis")
library(tidyverse)
library(dplyr)
library(lme4)
library(readr)
library(tidyr)
library(ggplot2)
library(sjPlot)
library(sjmisc)
library(Hmisc)
#library(plyr)
library(RColorBrewer)
library(reshape2)
choice = read.csv('C:/Users/Christine/Box Sync/data/mem_dm/cleaned_choice.csv')
rating = read.csv('C:/Users/Christine/Box Sync/data/mem_dm/cleaned_rating.csv')
mem = mem = read.csv('C:/Users/Christine/Box Sync/data/mem_dm/mem.csv')
```

## Correlations between value and memorability for each image

There's no significant correlations between averaged value and memorability

```{r, warning = FALSE}
#calculate mean values for each stimuli
values = rating %>% dplyr::group_by(image) %>% dplyr::summarise(value = mean(response))
values = values %>% mutate(stimuli = str_replace(image, 'https://voices.uchicago.edu/bakkourlab/files/2019/04/',  ''))

values_mem = merge(values, mem, by.x = 'stimuli', by.y = 'X', sort = TRUE)

cor.test(x = values_mem$value, y = values_mem$Memorability)
cor.test(x = choice$delta.value, y = choice$delta.mem)
```

## Z-scoring values and check distributions

The distribution of ratings are not normal, some of them have a lot of extreme values
Is there any way to make them more matched?
```{r, warning = FALSE}
## z-score memorability
mem = mem %>% mutate(z.mem = scale(Memorability)) %>% 
  mutate(image = paste("https://voices.uchicago.edu/bakkourlab/files/2019/04/", X, sep = ""))
mem.merge = mem[c('z.mem', 'image')]

choice.z = merge(mem.merge, choice, by.x = 'image', by.y = 'stim_left')
choice.z = choice.z %>% rename(stim_left = image, z.mem.l = z.mem)
choice.z = merge(mem.merge, choice.z, by.x = 'image', by.y = 'stim_right')
choice.z = choice.z %>% rename(stim_right = image, z.mem.r = z.mem)
#calculate z delta mem
choice.z = choice.z %>% mutate(z.delta.mem = z.mem.r-z.mem.l)
cor.test(x = choice.z$z.delta.value, y = choice.z$z.delta.mem, method = "pearson")

rating %>% dplyr::group_by(ID) %>% ggplot(aes(x = z, group = ID)) + 
  geom_histogram() + 
  facet_wrap(~ID)

```


## Calculate value x memorability

Surprisingly, memorability weighted value cannot predict choices

```{r, warning = FALSE}
# calculate weighted memorability by using value*mem for left and right stimuli
choice.z = choice.z %>% mutate(weighted.value.l = as.numeric(value_left)*as.numeric(mem_left),
                               weighted.value.r = as.numeric(value_right)*as.numeric(mem_right),
                               )
choice.z = choice.z %>% mutate(delta.w.v = weighted.value.r-weighted.value.l)

m1 = glmer(choseright~1+delta.value+delta.w.v+(1|ID), 
           data = choice.z, family = "binomial")
summary(m1)

```

## Interaction effect of z-scored delta value and delta mem

No interaction effect found

```{r}
m2 = glmer(choseright~1+z.delta.mem*z.delta.value+(1+z.delta.mem*z.delta.value|ID), 
           data = choice.z, family = "binomial")
summary(m2)
plot_model(m2)
plot_model(m2, type = "pred")
```

## Model for RT

```{r}
## model for RT
choice.z = choice.z %>% mutate(abs.delta.v.z = abs(z.delta.value))
m3 = glm(rt~1+z.delta.mem*abs.delta.v.z+(1+z.delta.mem*abs.delta.v.z|ID), 
           data = choice.z)
summary(m3)
plot_model(m3)
```

