---
title: "Analysis for Choice Task"
author: "Xinyue Li"
date: "2/16/2021"
output: html_document
---
# Analysis for Choice Task
Setup and preprocess data

```{r setup, warning = FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(lme4)
library(readr)
library(tidyr)
library(ggplot2)
library(sjPlot)
library(sjmisc)
library(Hmisc)
#library(plyr)
library(RColorBrewer)
library(reshape2)

#load raw dataset
dat = read.csv("C:/Users/Christine/Box Sync/data/mem_dm/full_data_dm_3_12.csv")

#create unique id for each subject
dat$ID = cumsum(!duplicated(dat[c('run_id', 'batch_id')]))

code = dat %>% filter(completioncode !='"')
age = dat %>% filter(ttype =='completion')
rating = dat %>% filter(ttype == 'rating_task')

#select and clean choice trials
choice = dat %>% filter(ttype == 'choice_task')
choice = choice %>% filter(rt != "null") %>% 
  mutate(rt = as.numeric(rt)) %>% 
  mutate(delta.value = as.numeric(value_right) - as.numeric(value_left)) %>% 
  mutate(delta.mem = as.numeric(mem_right) - as.numeric(mem_left)) %>% 
  mutate(choseright = case_when(key_press == 75 ~ 1, key_press ==74 ~ 0)) %>%
  mutate(abs.mem = abs(delta.mem))

#filter out participants who are 2 sd away from the probability of choosing right/left
choice.prob = choice %>% group_by(ID) %>% dplyr::summarize(right.choice = sum(choseright), right.prob = right.choice/138)
mean.p = mean(choice$choseright)
sd.p = sd(choice.prob$right.prob)
choice.ex.prob = choice.prob %>% filter(abs(right.prob-mean.p)<= 2*sd.p)####
choice = filter(choice, (ID %in% choice.ex.prob$ID))

#filter out participants with RT <300 trials
choice.rtfiltered = choice%>% filter(rt>=300)
choice.rtid =  choice.rtfiltered %>%dplyr::group_by(ID) %>% dplyr::summarise(RT = mean(as.numeric(rt)), n = n())
id.filtered = choice.rtid$ID[choice.rtid$n>=69]
choice = filter(choice.rtfiltered, (ID %in% id.filtered))

#mark trials when participants choose more memorable item
choice = choice %>% mutate(chosehigh.mem = case_when(choseright == 1 & delta.mem >=0 ~ 1, choseright == 0 & delta.mem <0 ~ 1, choseright == 1 & delta.mem <0 ~ 0,choseright == 0 & delta.mem >=0 ~ 0 ))

```



## Exclusion Processes

Calculated logistic regressions of `choice ~ delta value` for each participant, exclude those who had negative beta values, and those who had p values < 0.05, since they should make choices in accord with their rated subjective value if they actually paied attention to the task.

```{r, warning = FALSE}
# exclude based on beta in logistical regression
choice.beta = data.frame(ID=double(),
                         beta=double(),
                         p=double(),
                         stringsAsFactors=FALSE)[1:length(id.filtered),]
#calculate beta and p for each subject
for (i in 1:length(id.filtered)) {
  d =  choice %>% filter(ID == id.filtered[i], is.na(choseright)==FALSE)
  logistic = glm(choseright ~ 1 + delta.value, data = d, family = "binomial")
  beta = summary(logistic)[['coefficients']][2,1]
  p = summary(logistic)[['coefficients']][2,4]
  choice.beta$ID[i] = id.filtered[i]
  choice.beta$beta[i] = beta
  choice.beta$p[i] = p
}

filtered.b = choice.beta %>% filter(beta>0, p<0.05)

#plot regression lines in z-scored r
choice = choice %>% dplyr::group_by(ID) %>% dplyr::mutate(z.delta.value = scale(delta.value))
choice %>% group_by(ID) %>% ggplot(aes(x = z.delta.value, y = choseright, group = ID)) + 
  geom_point() + 
  stat_smooth(method="glm", method.args=list(family="binomial"), se=FALSE)+
  facet_wrap(~ID)

#filter choice with beta >0 and p<0.05
choice = filter(choice, (ID %in% filtered.b$ID | ID %in% c(10, 56)))

#plot regression lines after filtering
choice %>% group_by(ID) %>% ggplot(aes(x = z.delta.value, y = choseright, group = ID)) + 
  geom_point() + 
  stat_smooth(method="glm", method.args=list(family="binomial"), se=FALSE)+
  facet_wrap(~ID)

#write cleaned and exclued data for further use
rating = filter(rating, (ID %in% filtered.b$ID | ID %in% c(10, 56))) %>% 
  mutate(response = as.numeric(response)) %>%
  group_by(ID) %>% mutate(z = scale(response))
write.csv(rating, 'C:/Users/Christine/Box Sync/data/mem_dm/cleaned_rating.csv')
write.csv(choice, 'C:/Users/Christine/Box Sync/data/mem_dm/cleaned_choice.csv')
```


## Distribution plots of delta value and delta memorability

These two plots show the distribution of delta memorability (memorability for more memorable item - less memorable item) and the distribution of delta value (value for more memorable item - value for less memorable item), for all choice pairs among participants.

```{r, warning = FALSE}
#plot abs delta mem
choice %>% ggplot(aes(x = abs.mem, fill=..count..))+
  geom_histogram(binwidth = 0.05)+
  theme_classic()+
  xlim(0,1)+
  ggtitle('Distirbution of Delta Memorbaility')+
  xlab('Delta Memorability')
  
#plot delta value where higher mem - lower mem
choice.memvalue =  choice %>%  mutate(value.highmem = case_when(mem_left >= mem_right ~ -delta.value, mem_left < mem_right ~ delta.value))
choice.memvalue =  choice.memvalue %>%  mutate(value.highmem = value.highmem/100)
choice.memvalue %>% ggplot(aes(x = value.highmem, fill=..count..))+
  geom_histogram(binwidth = 0.02)+
  theme_classic()+
  ggtitle('Distirbution of Delta Value')+
  xlim(-0.5,0.5)+
  xlab('Delta Value')


```

## Probability of Chosing right for high/low delta memorability 
Since we couldn't find any strong significance of delta memorability on choices, we're trying to find possible weaker effects. To achieve that we split the trials into high/low delta memorability based on its median within each participant, and compaired the p of choosing higher memorable items within each participant.

```{r choice, warning = FALSE， message = FALSE}
library(plyr)
#split trials into high/low delta mem based on within-subject median
choice = choice %>% 
  arrange(ID, abs.mem) %>% 
  group_by(ID) %>% 
  dplyr::mutate(rank = 1:n()) %>% 
  ungroup()
choice.low = choice %>% dplyr::group_by(ID) %>% slice(seq(0.5 * n())) %>% 
  mutate(bin.absmem = 1)
choice.high = choice %>% dplyr::group_by(ID) %>% slice(-seq(0.5 * n())) %>% 
  mutate(bin.absmem = 2)
choice = rbind(choice.high, choice.low)
table(choice$bin.absmem, choice$ID)

choice = choice %>% mutate(bin.absmem = as.factor(bin.absmem))

#for high/low delta mem plotting
choice.sub = choice %>% group_by(ID, bin.absmem) %>% dplyr::summarize(mem.choice = sum(chosehigh.mem), hmem.p = mem.choice/n())

#plot high/low mem
binned.high.low = choice %>% group_by(bin.absmem) %>% dplyr::summarise(count = sum(chosehigh.mem), mean.mem = mean(abs.mem), n = n(), p = count/n)
binned.high.low = binned.high.low %>% mutate(bin.absmem = as.factor(bin.absmem))
binned.high.image = choice %>% group_by(bin.absmem, ID) %>% dplyr::summarise(count = sum(chosehigh.mem), mean.mem = mean(abs.mem), n = n(), p = count/n)
 

binned.high.image %>% ggplot(aes( x = bin.absmem, y = p, fill = factor(bin.absmem)))+
  geom_bar(stat="summary", alpha = .3, show.legend = FALSE)+
  geom_point(aes(y = p, color = bin.absmem), position = position_jitter(width = .15), size = 2, alpha = 0.8, show.legend = FALSE) +
  labs(fill='High/Low memorability') +
  theme_classic()+
  ggtitle("Probability of Choosing Higher Memorable Item")+
  geom_line(aes(group = ID),alpha = 0.3)+
  scale_x_discrete(labels=c("1" = "Low", "2" = "High"), name = "Delta Memorability")

```


```{r , include = FALSE}
#Create raincloud theme
"%||%" <- function(a, b) {
  if (!is.null(a)) a else b
}

geom_flat_violin <- function(mapping = NULL, data = NULL, stat = "ydensity",
                             position = "dodge", trim = TRUE, scale = "area",
                             show.legend = NA, inherit.aes = TRUE, ...) {
  layer(
    data = data,
    mapping = mapping,
    stat = stat,
    geom = GeomFlatViolin,
    position = position,
    show.legend = show.legend,
    inherit.aes = inherit.aes,
    params = list(
      trim = trim,
      scale = scale,
      ...
    )
  )
}

#' @rdname ggplot2-ggproto
#' @format NULL
#' @usage NULL
#' @export
GeomFlatViolin <-
  ggproto("GeomFlatViolin", Geom,
          setup_data = function(data, params) {
            data$width <- data$width %||%
              params$width %||% (resolution(data$x, FALSE) * 0.9)
            
            # ymin, ymax, xmin, and xmax define the bounding rectangle for each group
            data %>%
              group_by(group) %>%
              mutate(ymin = min(y),
                     ymax = max(y),
                     xmin = x,
                     xmax = x + width / 2)
          },
  
  draw_group = function(data, panel_scales, coord) {
    # Find the points for the line to go all the way around
    data <- transform(data, xminv = x,
                      xmaxv = x + violinwidth * (xmax - x))
    
    # Make sure it's sorted properly to draw the outline
    newdata <- rbind(plyr::arrange(transform(data, x = xminv), y),
                     plyr::arrange(transform(data, x = xmaxv), -y))
    
    # Close the polygon: set first and last point the same
    # Needed for coord_polar and such
    newdata <- rbind(newdata, newdata[1,])
    
    ggplot2:::ggname("geom_flat_violin", GeomPolygon$draw_panel(newdata, panel_scales, coord))
  },
  
  draw_key = draw_key_polygon,
  
  default_aes = aes(weight = 1, colour = "grey20", fill = "white", size = 0.5,
                    alpha = NA, linetype = "solid"),
  
  required_aes = c("x", "y")
  )

raincloud_theme <- theme(
  text = element_text(size = 10),
  axis.title.x = element_text(size = 16),
  axis.title.y = element_text(size = 16),
  axis.text = element_text(size = 14),
  axis.text.x = element_text(angle = 45, vjust = 0.5),
  legend.title = element_text(size = 16),
  legend.text = element_text(size = 16),
  legend.position = "right",
  plot.title = element_text(lineheight = .8, face = "bold", size = 16),
  panel.border = element_blank(),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  axis.line.x = element_line(colour = "black", size = 0.5, linetype = "solid"),
  axis.line.y = element_line(colour = "black", size = 0.5, linetype = "solid"))

```


The raincloud plot for high/low delta memorability differences

```{r, warning = FALSE}
g = ggplot(data = choice.sub, aes(y = hmem.p, x = as.factor(bin.absmem), fill = as.factor(bin.absmem), group=as.factor(bin.absmem))) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8, show.legend = FALSE) +
  geom_point(aes(y = hmem.p, color = as.factor(bin.absmem)), position = position_jitter(width = .15), size = .5, alpha = 0.8, show.legend = FALSE) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5, show.legend = FALSE) +
  #expand_limits(x = 5.25) +
  #guides(fill = FALSE) +
  #guides(color = FALSE) +
  ylab('p')+
  xlim(-1, 2)+
 # labs(fill='High/Low mem') +
  theme_bw() +
 # geom_line(aes(group = ID),alpha = 0.3)+
  scale_x_discrete(labels=c("1" = "Low", "2" = "High"), name = "Delta Memorability")+
  raincloud_theme

g

```



## Model Fitting
Fitted mixted effects model for delta memorability and delta value, and found no effect of delta mem, but strong effect of delta value for predicting the behavior

```{r, warning = FALSE}
#mixted effects model for delta mem and delta value
m1 = glmer(choseright~1+delta.mem+delta.value+(1+delta.mem+delta.value|ID), data = choice, family = "binomial")
summary(m1)

plot_model(m1)
plot_model(m1, type = "pred")

```

Plot for random effects
```{r}
library(glmmTMB)
plot_model(m1, type = "re")

```


