---
title: "Analysis for Choice Task"
author: "Xinyue Li"
date: "2/16/2021"
output: html_document
---
## Analysis for Choice Task
Setup and preprocess data

```{r setup, warning = FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/Christine/Desktop/python/dm/data_analysis/data/2_24/")
library(tidyverse)
library(dplyr)
library(lme4)
library(readr)
library(tidyr)
library(ggplot2)
library(sjPlot)
library(sjmisc)
library(Hmisc)
#library(plyr)
library(RColorBrewer)
library(reshape2)

dat = read.csv("C:/Users/Christine/Desktop/python/dm/data_analysis/data/2_24/food-pairs-choice-task-with-age-check-edited-20.csv")
dat = dat %>% mutate(batch_id = 1)
#filter out the first batch
#dat = dat %>% filter(batch_id != 2)
#create unique id for each subject
dat$ID = cumsum(!duplicated(dat['run_id']))
#get code
code = dat %>% filter(completioncode !='"')
age = dat %>% filter(ttype =='completion')
rating = dat %>% filter(ttype == 'rating_task')

choice = dat %>% filter(ttype == 'choice_task')
choice = choice %>% filter(rt != "null")
choice = choice %>% mutate(rt = as.numeric(rt))
choice = choice %>% mutate(delta.value = as.numeric(value_right) - as.numeric(value_left))
choice = choice %>% mutate(delta.mem = as.numeric(mem_right) - as.numeric(mem_left))
choice = choice %>% mutate(choseright = case_when(key_press == 75 ~ 1, key_press ==74 ~ 0))
choice = choice %>% mutate(bin.mem=ntile(choice$delta.mem, 5))
choice = choice %>% mutate(bin.rt=ntile(choice$rt, 5))
choice = choice %>% mutate(abs.mem = abs(delta.mem))

#filter participants who are 2 sd away from the probability of choosing right/left
choice.prob = choice %>% group_by(ID) %>% dplyr::summarize(right.choice = sum(choseright), right.prob = right.choice/138)
mean.p = mean(choice$choseright)
sd.p = sd(choice.prob$right.prob)
choice.ex.prob = choice.prob %>% filter(abs(right.prob-mean.p)<= 2*sd.p)####
choice = filter(choice, (ID %in% choice.ex.prob$ID))

#filter participants with RT <300 trials
choice.rtfiltered = choice%>% filter(rt>=300)
choice.rtid =  choice.rtfiltered %>%dplyr::group_by(ID) %>% dplyr::summarise(RT = mean(as.numeric(rt)), n = n())
id.filtered = choice.rtid$ID[choice.rtid$n>=69]
choice = filter(choice.rtfiltered, (ID %in% id.filtered))


choice = choice %>% mutate(chosehigh.mem = case_when(choseright == 1 & delta.mem >=0 ~ 1, choseright == 0 & delta.mem <0 ~ 1, choseright == 1 & delta.mem <0 ~ 0,choseright == 0 & delta.mem >=0 ~ 0 ))

```



#Filtered data has 40 participants in total


The following table shows when the trials are split into high/low delta memorability, the counts of high/low trials corresponding to each subject ID.

```{r, warning = FALSE}
#split trials into high/low delta mem based on within-subject median
choice = choice %>% 
  arrange(ID, abs.mem) %>% 
  group_by(ID) %>% 
  dplyr::mutate(rank = 1:n()) %>% 
  ungroup()
choice.low = choice %>% dplyr::group_by(ID) %>% slice(seq(0.5 * n()))
choice.low = choice.low %>% mutate(bin.absmem = 1)
choice.high = choice %>% dplyr::group_by(ID) %>% slice(-seq(0.5 * n()))
choice.high = choice.high %>% mutate(bin.absmem = 2)
choice = rbind(choice.high, choice.low)
table(choice$bin.absmem, choice$ID)

choice = choice %>% mutate(bin.absmem = as.factor(bin.absmem))

#for high/low delta mem plotting
choice.sub = choice %>% group_by(ID, bin.absmem) %>% dplyr::summarize(mem.choice = sum(chosehigh.mem), hmem.p = mem.choice/n())

binned.choice = choice %>% group_by(bin.mem) %>% 
  dplyr::summarise(delta = mean(delta.value), RT = mean(as.numeric(rt)), MEM = mean(as.numeric(delta.mem)), n = n(), right = sum(choseright)) %>%
  mutate(p = right/n)
```


Distribution plots of delta value and delta memorability

```{r, warning = FALSE}
#plot abs delta mem
choice %>% ggplot(aes(x = abs.mem, fill=..count..))+
  geom_histogram(binwidth = 0.05)+
  theme_classic()+
  xlim(0,1)+
  ggtitle('Distirbution of Delta Memorbaility')+
  xlab('Delta Memorability')
  
# plot delta value where higher mem - lower mem
choice.memvalue =  choice %>%  mutate(value.highmem = case_when(mem_left >= mem_right ~ -delta.value, mem_left < mem_right ~ delta.value))
choice.memvalue =  choice.memvalue %>%  mutate(value.highmem = value.highmem/100)
choice.memvalue %>% ggplot(aes(x = value.highmem, fill=..count..))+
  geom_histogram(binwidth = 0.02)+
  theme_classic()+
  ggtitle('Distirbution of Delta Value')+
  xlim(-0.5,0.5)+
  xlab('Delta Value')


```

Split the trials into high/low memorability based on its median within each participant

```{r choice, warning = FALSE， message = FALSE}
library(plyr)
#plot high/low mem
binned.high.low = choice %>% group_by(bin.absmem) %>% dplyr::summarise(count = sum(chosehigh.mem), mean.mem = mean(abs.mem), n = n(), p = count/n)
binned.high.low = binned.high.low %>% mutate(bin.absmem = as.factor(bin.absmem))
binned.high.image = choice %>% group_by(bin.absmem, ID) %>% dplyr::summarise(count = sum(chosehigh.mem), mean.mem = mean(abs.mem), n = n(), p = count/n)
 

binned.high.image %>% ggplot(aes( x = bin.absmem, y = p, fill = factor(bin.absmem)))+
  geom_bar(stat="summary", alpha = .3, show.legend = FALSE)+
  geom_point(aes(y = p, color = bin.absmem), position = position_jitter(width = .15), size = 2, alpha = 0.8, show.legend = FALSE) +
  labs(fill='High/Low memorability') +
  theme_classic()+
  ggtitle("Probability of Choosing Higher Memorable Item")+
  geom_line(aes(group = ID),alpha = 0.3)+
  scale_x_discrete(labels=c("1" = "Low", "2" = "High"), name = "Delta Memorability")

```


```{r , include = FALSE}
#Create raincloud theme
"%||%" <- function(a, b) {
  if (!is.null(a)) a else b
}

geom_flat_violin <- function(mapping = NULL, data = NULL, stat = "ydensity",
                             position = "dodge", trim = TRUE, scale = "area",
                             show.legend = NA, inherit.aes = TRUE, ...) {
  layer(
    data = data,
    mapping = mapping,
    stat = stat,
    geom = GeomFlatViolin,
    position = position,
    show.legend = show.legend,
    inherit.aes = inherit.aes,
    params = list(
      trim = trim,
      scale = scale,
      ...
    )
  )
}

#' @rdname ggplot2-ggproto
#' @format NULL
#' @usage NULL
#' @export
GeomFlatViolin <-
  ggproto("GeomFlatViolin", Geom,
          setup_data = function(data, params) {
            data$width <- data$width %||%
              params$width %||% (resolution(data$x, FALSE) * 0.9)
            
            # ymin, ymax, xmin, and xmax define the bounding rectangle for each group
            data %>%
              group_by(group) %>%
              mutate(ymin = min(y),
                     ymax = max(y),
                     xmin = x,
                     xmax = x + width / 2)
          },
  
  draw_group = function(data, panel_scales, coord) {
    # Find the points for the line to go all the way around
    data <- transform(data, xminv = x,
                      xmaxv = x + violinwidth * (xmax - x))
    
    # Make sure it's sorted properly to draw the outline
    newdata <- rbind(plyr::arrange(transform(data, x = xminv), y),
                     plyr::arrange(transform(data, x = xmaxv), -y))
    
    # Close the polygon: set first and last point the same
    # Needed for coord_polar and such
    newdata <- rbind(newdata, newdata[1,])
    
    ggplot2:::ggname("geom_flat_violin", GeomPolygon$draw_panel(newdata, panel_scales, coord))
  },
  
  draw_key = draw_key_polygon,
  
  default_aes = aes(weight = 1, colour = "grey20", fill = "white", size = 0.5,
                    alpha = NA, linetype = "solid"),
  
  required_aes = c("x", "y")
  )

raincloud_theme <- theme(
  text = element_text(size = 10),
  axis.title.x = element_text(size = 16),
  axis.title.y = element_text(size = 16),
  axis.text = element_text(size = 14),
  axis.text.x = element_text(angle = 45, vjust = 0.5),
  legend.title = element_text(size = 16),
  legend.text = element_text(size = 16),
  legend.position = "right",
  plot.title = element_text(lineheight = .8, face = "bold", size = 16),
  panel.border = element_blank(),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  axis.line.x = element_line(colour = "black", size = 0.5, linetype = "solid"),
  axis.line.y = element_line(colour = "black", size = 0.5, linetype = "solid"))

```


The raincloud plot for high/low delta memorability

```{r, warning = FALSE}
g <- ggplot(data = choice.sub, aes(y = hmem.p, x = as.factor(bin.absmem), fill = as.factor(bin.absmem), group=as.factor(bin.absmem))) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8, show.legend = FALSE) +
  geom_point(aes(y = hmem.p, color = as.factor(bin.absmem)), position = position_jitter(width = .15), size = .5, alpha = 0.8, show.legend = FALSE) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5, show.legend = FALSE) +
  #expand_limits(x = 5.25) +
  #guides(fill = FALSE) +
  #guides(color = FALSE) +
  ylab('p')+
  xlim(-1, 2)+
 # labs(fill='High/Low mem') +
  theme_bw() +
 # geom_line(aes(group = ID),alpha = 0.3)+
  scale_x_discrete(labels=c("1" = "Low", "2" = "High"), name = "Delta Memorability")+
  raincloud_theme

g

```



## Model Fitting
```{r, warning = FALSE}
m1 = glmer(choseright~1+delta.mem+delta.value+(1+delta.mem+delta.value|ID), data = choice, family = "binomial")
summary(m1)

plot_model(m1)
plot_model(m1, type = "pred")

```

```{r}
library(glmmTMB)
plot_model(m1, type = "re")

```


