---
title: "Visualization"
author: "Xinyue Li"
date: "4/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/Christine/src/mem_dm/Choice_task_analysis")
library(tidyverse)
library(dplyr)
library(lme4)
library(readr)
library(tidyr)
library(ggplot2)
library(sjPlot)
library(sjmisc)
library(Hmisc)
#library(plyr)
library(RColorBrewer)
library(reshape2)
library(corrplot)
require(gridExtra)

#loading data files
choice = read.csv('C:/Users/Christine/Box Sync/data/mem_dm/cleaned_choice.csv')
rating = read.csv('C:/Users/Christine/Box Sync/data/mem_dm/cleaned_rating.csv')
mem = read.csv('C:/Users/Christine/Box Sync/data/mem_dm/mem.csv')
food = read.csv("C:/Users/Christine/Box Sync/data/mem_dm/stimchar_final_touse.csv")
food = food %>% filter(age == "18-25" | age == "26-30" | age == "31-35")
food.mean = food %>% group_by(stimulus) %>% dplyr::summarize(tasty = mean(rating.tasty),pref = mean(choice.rating))
mem = merge(food.mean, mem, by = 'stimulus')

```

## Visualization figures for MA thesis

Figure 1. Histogram for distribution of memorability

The vertical line represents for the median of memorability scores = 0.48

```{r}
## ggplot histogram
ggplot(mem, aes(x=Memorability)) + 
  geom_histogram(color="steelblue", fill="white", bins = 25) + 
  geom_vline(xintercept = 0.48,linetype = "dashed") +
  theme_bw()
```


## Correlation Matrix

Figure 2. Plot for correlation matrix between 17 ratings and memorbaility
Had a prettier version on Python

```{r pressure, echo=FALSE}
rdat = food %>% dplyr::select(stimulus, choice.rating, starts_with("rating"))
colnames(rdat) = sub("rating[.]", "", colnames(rdat))
colnames(rdat) = sub("[.]rating", "", colnames(rdat))

#rdat$sugar = 10 - rdat$sugar
#rdat$disgusting = 10 - rdat$disgusting
#rdat$healthy = 10 - rdat$healthy
#rdat$vitamins = 10 - rdat$vitamins

# rename
#cinds = sapply(c("sugar", "disgusting", "healthy", "vitamins"), function(x) which(colnames(rdat) == x))
#colnames(rdat)[cinds] = c("low-sugar", "not-disgusting", "unhealthy", "low-vitamins")

rmat = as.matrix(rdat[,-1])
rownames(rmat) = rdat$stimulus
rmat.nochoice = rmat[,-1]

new.ord = c("tasty", "othertasty", "feel", "texture", "disgusting", "familiar", "filling", "healthy", "sweetsaltysavory", "calories", "carbohydrates", "fat", "vitamins", "gluten", "sodium", "sugar", "protein", "stimulus")


# correlation matrix with memorability score
ave.mat.r = rdat[,new.ord] %>% 
  group_by(stimulus) %>% 
  summarise_all(mean) 
# matching memorability stimulus name to food data stimulus name
ave.mat.r = data.frame(Memorability = mem$Memorability, mem.stimulus = mem$X, ave.mat.r)

M.mem = ave.mat.r %>% dplyr::select(-mem.stimulus, -stimulus) %>% cor()
diag(M.mem) = 0
corrplot(M.mem, method="circle", diag = F, #order="hclust", 
         #is.corr=F, cl.lim=c(-0.85,0.85), 
         col=rev(colorRampPalette(brewer.pal(n=11, name="RdBu"))(256)))
```


## Scatter plot

Figure 3. Scatter plot for memorability scores and averaged tastiness score for the factor analysis on each food item. 

```{r sactter, warning=FALSE}
# factor analysis
nFactors::nCng(as.data.frame(rmat.nochoice), model="factors") 
fit <- factanal(rmat.nochoice, 3, scores="regression")

scores3 <- fit$scores
ind1 <- which.max(fit$loadings[rownames(fit$loadings) == "unhealthy",])
ind2 <- which.max(fit$loadings[rownames(fit$loadings) == "tasty",])
ind3 <- which.max(fit$loadings[rownames(fit$loadings) == "sweetsaltysavory",])
colnames(scores3) <- c("Food.UnHealth", "Food.Taste", "Food.SweetProtein")
outdf <- data.frame(subjectId=food$subjectId, stimulus=food$stimulus, scores3)

# score of factor for each food item
ave.factor = outdf %>% group_by(stimulus) %>% 
  summarise_all(mean) 

# add mem score to the factor data frame
labels = sapply(mem$stimulus, function(x) which(ave.factor$stimulus == x))
ave.factor.mem = data.frame(Memorability = mem$Memorability, mem.stimulus = mem$X, ave.factor)

# perform linear regression
fit1 = lm(Memorability ~ Food.Taste + Food.UnHealth + Food.SweetProtein, data = ave.factor.mem)
#summary(fit1)

# plot mem~food.taste
ave.factor.mem %>% ggplot(aes(x = Food.Taste, y = Memorability))+
  geom_point(size = 3, alpha = 0.5, color = "steelblue3", fill = "steelblue")+
  geom_smooth(method='lm')+
  xlab('Tastiness')+
  theme_bw()

```

# Experiment 2 Figures

## choseright ~ delta mem / delta value

Trying to implement binned raw data into it

```{r z_score, include=FALSE}

values = rating %>% dplyr::group_by(image) %>% dplyr::summarise(value = mean(response))
values = values %>% mutate(stimuli = str_replace(image, 'https://voices.uchicago.edu/bakkourlab/files/2019/04/',  ''))
values_mem = merge(values, mem, by.x = 'stimuli', by.y = 'X', sort = TRUE)

## z-score memorability
mem = mem %>% mutate(z.mem = scale(Memorability)) %>% 
  mutate(image = paste("https://voices.uchicago.edu/bakkourlab/files/2019/04/", X, sep = ""))
mem.merge = mem[c('z.mem', 'image', 'tasty', 'pref')]

choice.z = merge(mem.merge, choice, by.x = 'image', by.y = 'stim_left') %>% 
  rename(stim_left = image, z.mem.l = z.mem, tasty.l = tasty, pref.l = pref)
choice.z = merge(mem.merge, choice.z, by.x = 'image', by.y = 'stim_right') %>% 
  rename(stim_right = image, z.mem.r = z.mem, tasty.r = tasty, pref.r = pref)
#calculate z delta mem
choice.z = choice.z %>% mutate(z.delta.mem = z.mem.r-z.mem.l,
                               delta.tasty = tasty.r - tasty.l,
                               delta.pref = pref.r - pref.l)

## z-score values for each subject
#calculate z scores within each ID
rating.merge = rating[c('ID', 'z', 'image')]
rating.merge.l = rating.merge %>% rename(stim_left = image)
rating.merge.r = rating.merge %>% rename(stim_right = image)

#merge columns based on ID and stimuli names
choice.z = merge(rating.merge.l, choice.z, by = c('ID', 'stim_left')) %>%
  rename(z.value.l = z)
choice.z = merge(rating.merge.r, choice.z, by = c('ID', 'stim_right')) %>% 
  rename(z.value.r = z)
choice.z = choice.z %>% mutate(z.delta.value = z.value.r - z.value.l)

```
Generate the interaction model

```{r choise_plot}
#generate the model
m2 = glmer(choseright~1+z.delta.mem*z.delta.value+(1+z.delta.mem*z.delta.value|ID), 
           data = choice.z, family = "binomial")
#summary(m2)
#plt.value = plot_model(m2, type = "pred", terms="z.delta.value [all]")
#plt.mem = plot_model(m2, type = "pred", terms="z.delta.mem [all]")

```

Plot the single effect model for delta mem

```{r}
#single model for delta mem
m2.mem = glmer(choseright~1+z.delta.mem+(1+z.delta.mem|ID), 
           data = choice.z, family = "binomial")
#summary(m2.mem)
plt.mem.c = plot_model(m2.mem, type = "pred", terms="z.delta.mem [all]")
plt.mem.c
```

Plot the single effect model for delta value

```{r}
#single model for delta value
m2.value = glmer(choseright~1+z.delta.value+(1+z.delta.value|ID), 
           data = choice.z, family = "binomial")
#summary(m2.value)
plt.value.c = plot_model(m2.value, type = "pred", terms="z.delta.value [all]")
plt.value.c

#anova(m2.value, m2)
```

### Organize the figures together and add actual data points on them

```{r}

plt.mem.c = plt.mem.c + scale_y_continuous(labels = scales::percent, limits = c(0,1)) +
  xlab("Delta Memorability")

plt.value.c = plt.value.c + xlab("Delta Value")

grid.arrange(plt.mem.c, plt.value.c, ncol=2)


```


```{r}
## test for creating actual data figure

choice.z = choice.z %>% mutate(bin.v=ntile(choice.z$z.delta.value, 5)) %>%
  mutate(bin.m=ntile(choice.z$z.delta.mem, 5))

binned.choice = choice.z %>% group_by(bin.m) %>% 
  dplyr::summarise(delta = mean(z.delta.value), RT = mean(as.numeric(rt)), n = n(), right = sum(choseright), MEM = mean(z.delta.mem)) %>%
  mutate(p = right/n)

dat.p.m = binned.choice %>% ggplot(aes(x = MEM, y = p))+
  geom_point()+
  scale_y_continuous(labels = scales::percent, limits = c(0,1))+
  scale_x_continuous(limits = c(-6,6))+
  theme_classic()

dat.p.m



```

